### 2015-02-22 fundamentals/impl.tex

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may supply both a natural uranium
and SWU constraint. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.

Finally, requesting facilities, institutions and regions may apply
\textit{preferences} to each potential request-bid pairing based on the proposed
resource transfer. Therefore, an institution can apply a higher preference to a
partner to which it is congenial; similarly, a region may negate any transfers
of material which have a higher uranium enrichment than is allowable.

@@

The current \Cycamore release provide basic functionality, As illustrated in
Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
functionality enabling simple fuel cycle analyses. As future contributions are
vetted, the capabilities in \Cycamore may grow.

@@

Regression tests ensure unexpected backwards-incompatible changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting simulations.

>>>>

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
attach such constraints to its bids. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.

Finally, requesting facilities, institutions and regions may apply
\textit{preferences} to each potential request-bid pairing based on the proposed
resource transfer. Facilities can apply arbitrary complex logic to rank the bids
that they have received, whether based on the quantity available in each bid or
on the quality of each bid, and the consequent implications of the physics behavior
of that facility. In addition, an institution can apply a higher preference to a
partner to which it is congenial; similarly, a region may negate any transfers
of material which have a higher uranium enrichment than is allowable.

@@

As illustrated in
Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
functionality enabling simple fuel cycle analyses. As future contributions are
vetted, the capabilities in \Cycamore may grow.

@@

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting simulations.
